Soss

### 2019-12-30 paper/paper.tex
fix compile error
two-way anova model

\usepackage[ruled]{algorithm2e} 
%\usepackage{parskip}
\usepackage{backnaur}
\usepackage{jlcode}
\usepackage{todonotes}
\usepackage{textalpha}

@@

\begin{lstlisting}[language = Julia]
m = @model n begin
    x ~ Normal(0,10) |> iid(n)
    α ~ Normal()
    β ~ Normal()
    σ ~ HalfNormal()
    yhat = α .+ β .* x
    y ~ For(n) do j 
            Normal(yhat[j],σ)
        end
end
\end{lstlisting}

@@

\[
  \ell =
  - 0.5 α^{2} 
  - 0.5 β^{2}
  - σ^{2} 
  + \sum_{\left(j_{1}\right)=1}^{n} \left(- \log{\left(\sigma \right)} 
  - \frac{\log{\left(\pi \right)}}{2} 
  - \frac{\log{\left(2 \right)}}{2} 
  - \frac{\left({y}_{\left(j_{1}\right)} 
  - {\hat{y}}_{\left(j_{1}\right)}\right)^{2}}{2 \sigma^{2}}\right) 
  + \sum_{j_{1}=1}^{n} \left(- 0.005 {x}_{j_{1}}^{2} 
  - 2.99573227355399 
  - \frac{\log{\left(\pi \right)}}{2} 
  + \frac{\log{\left(2 \right)}}{2}\right) 
  - 2 \log{\left(\pi \right)} 
  - 1.38629436111989
\]

>>>>

\usepackage[ruled]{algorithm2e} 
%\usepackage{parskip}
\usepackage{backnaur}
\usepackage{jlcode}
\usepackage{todonotes}
% \usepackage{textalpha}
\usepackage{tikz}
\usetikzlibrary{bayesnet}

@@

\begin{tikzpicture}

    \node[obs] (y) {$y$};
    \node[det, above=of y] (yhat) {$\hat{y}$};
    \node[latent, left=of yhat] (epsi) {$\varepsilon_I$};
    \node[latent, above=of yhat] (alpha) {$\alpha$};
    \node[latent, right=of yhat] (epsj) {$\varepsilon_J$};
    \node[latent, left=of alpha] (sigi) {$\sigma_I$};
    \node[latent, right=of alpha] (sigj) {$\sigma_J$};
    \node[latent, below=of y] (sigma) {$\sigma$};

    \edge {sigi} {epsi};
    \edge {sigj} {epsj};
    \edge {sigma, yhat} {y};
    \edge {alpha} {sigi};
    \edge {alpha} {sigj};
    \edge {epsi,epsj} {yhat};

    \plate {I} {(y)(yhat)(epsi)} {$I$};
    \plate {J} {(y)(yhat)(epsj)(I.north east)} {$J$};

  \end{tikzpicture}

\begin{lstlisting}[language = Julia]

m = @model I,J begin
    α ~ HalfCauchy()
    σi ~ HalfNormal(α)
    σj ~ HalfNormal(α)

    εi ~ Normal(0, σi) |> iid(I)
    εj ~ Normal(0, σj) |> iid(J)
    yhat = εz .+ εy'
    σ ~ HalfNormal()
    y ~ For(I,J) do i,j 
            Normal(yhat[i,j], σ)
        end
end
\end{lstlisting}

@@

\[
    \ell = \beta
    - 0.5 \alpha^{2} 
    - 0.5 \beta^{2}
    - \sigma^{2} 
    + \sum_{\left(j_{1}\right)=1}^{n} \left(
        - \log{\left(\sigma \right)} 
        - \frac{\log{\left(\pi \right)}}{2} 
        - \frac{\log{\left(2 \right)}}{2} 
        - \frac{\left({y}_{\left(j_{1}\right)} 
        - {\hat{y}}_{\left(j_{1}\right)}\right)^{2}}{2 \sigma^{2}}
        \right) 
    + \sum_{j_{1}=1}^{n} \left(
        - 0.005 {x}_{j_{1}}^{2} 
        - 3.0 
        - \frac{\log{\left(\pi \right)}}{2} 
        + \frac{\log{\left(2 \right)}}{2}
        \right) 
    - 2 \log{\left(\pi \right)} 
    - 1.38629436111989
\]
